Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-10-10 manuscript.tex
overleaf update

\includegraphics[width=1\textwidth]{./figs_03/fig_intro_2_light.pdf}

>>>>

\hypertarget{fig:intro}{%
\begin{figure}
\centering
\includegraphics[width=1\textwidth]{./figs_03/fig_intro_2_light.pdf}
\caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) Diagram of the expiremental setup. WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp b) How bits are transmitted in M=16 PPM modulation. An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data. c) XXXXXXXX}
\label{fig:intro}
\end{figure}
}
